\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{hyperref}

\pagestyle{plain}
\setcounter{page}{1}
\pagenumbering{arabic}

\begin{document}

\name{Lijie Ren \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
6520 Cervantes Rd. Apt. 24       & lijie.cs@gmail.com \\
Isla Vista, CA 93117             & (1)-805-886-3519 \\
\end{tabular}


\section{\sc Programming Languages}
Extensive programming experiences with C/C++, Java, Python, Matlab. \\
Familiar with Ruby, HTML, CSS, PHP, JavaScript, etc.


\section{\sc Education}
{\bf University of California, Santa Barbara}, CA, USA\\
\vspace*{-.1in}
\begin{list1}
\item[] M.S., Computer Science (expected
  graduation date: Jun. 2012)
\begin{list2}
\vspace*{.05in}
\item GPA:  4.0/4.0
\end{list2}
\end{list1}

{\bf Shanghai Jiao Tong University}, Shanghai, China\\
\vspace*{-.1in}
\begin{list1}
\item[] B.E., Electrical Engineering,  Jun. 2009
\begin{list2}
\vspace*{.05in}
\item GPA:  3.5/4.0
\end{list2}
\end{list1}


\section{\sc Work Experiences}
{Google}, Tokyo, Japan\\
{\bf{\em Software Engineer Intern}} \hfill {\bf Jul. 2011 - Sep. 2011}\\
I worked in a project aiming to facilitate people's daily commuting. I significantly optimized the core algorithm used in the back-end and made major contributions to the design and implementation of two front-end Android applications.

\section{\sc Spare-Time Projects}
{\bf{\em LifeTrack}}  \hfill {\bf Dec. 2011 - Present}\\
An Android application that automatically generate a ``location diary'' of the user with super low power usage and an intuitive map view.

\section{\sc Research Projects}
{University of California, Santa Barbara}, CA, USA

\vspace{-.1cm}
{\bf{\em Next Generation ``Google Directions''}}  \hfill {\bf Oct. 2011 - Present}\\
I designed a new direction-query system which takes other users' queries into consideration in order to return more dynamic and accurate lowest-cost routes.


{\bf{\em Time-Dependent Shortest Paths}}  \hfill {\bf Jan. 2011 - Present}\\
I did scalable implementations of shortest-path algorithms on static and time-dependent graphs, using Combinatorial BLAS Library, a high performance parallel matrix-operation library in development at UCSB and several other organizations. Evaluations showed that the achieved performances were comparable to those observed in Google's Pregel System.


{\bf{\em Visibility-based Pursuit-Evasion Problem}}  \hfill {\bf Mar. 2011 - May. 2011}\\
I proved a lower bound of the number of robots needed to capture an evader with the same speed in any polygonal environment, possibly with holes.


%\vspace{-.1cm}
{\bf{\em Business Analytics on Social Networks}}  \hfill {\bf Aug. 2010 - Feb. 2011}\\
I optimized an algorithm that clusters people on social networks who make certain purchases. The optimization boosted the performance by 100\%.

%\vspace{-.1cm}
{\bf{\em Cloud Computing}}  \hfill {\bf Mar. 2010 - Aug. 2010}\\
I integrated Google App Engine's database backup/restore tool, BulkLoader, to Appscale, an open-source cloud computing platform in development at UCSB.

%\vspace{-.1cm}
{\bf{\em Graph Mining}}  \hfill {\bf Jan. 2010 - Mar. 2010}\\
I improved the famous graph mining algorithm, gSpan, to efficiently mine frequent graph patterns containing wildcard label *.

{Shanghai Jiao Tong University}, Shanghai, China

\vspace{-.3cm}
{\bf{\em Quantum Information Processing}} \hfill {\bf Sep .2007 - Jun. 2009}\\
I presented a mathematical framework for quantum teleportation on quantum graph states, which can be used for designing quantum entanglement states to transport quantum information, or for evaluating such capability of a given entanglement.
\vspace*{.05in}
\begin{list2}
\item Lijie Ren, Guangqiang He, Guihua Zeng: Universal Teleportation via Continuous-Variable Graph States. Physical Review A. (2008) 78, 042302.
\end{list2}

%\newpage
\section{\sc Teaching Experience}
{University of California, Santa Barbara}, CA, USA

\vspace{-.3cm}
{\bf {\em Teaching Assistant}} \hfill {\bf Sep. 2009  - present}\\
Duties at various times have included office hours and leading weekly discussion sections.
\vspace*{.05in}
\begin{list2}
\item {CS 263 Modern Programming Languages and Their
Implementations} \hfill {Winter 2011}\\
A graduate level course discussing the key implementation concepts in Java, Python, and C++.

\item {CS 231 Combinatorial Algorithms Topics} \hfill {Fall 2010}\\
A graduate level course discussing advanced combinatorial algorithms.

\item {CS 130B Data Structure and Algorithm II} \hfill {Winter 2010 \& Spring 2011}\\
An upper division course discussing classic algorithms.

\item {CS 40 Fundamental Computer Science} \hfill {Fall 2009 \& Spring 2010}\\
A lower division course about discrete mathematics.
\end{list2}

\section{\sc More \\About Me}
I am a pianist and an amateur photographer.\\
I am fluent in English and Mandarin. I am currently learning Japanese.

\end{resume}
\end{document}
